Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
r

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs,siunitx}
\usepackage{float}
\usepackage{caption}
\usepackage{footnote}
\makesavenoteenv{tabular}
\usepackage{tablefootnote}
\lhead{}
\rhead{}
\chead{Social Data Science, Summer 2019.}

@@

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real estate property valuations. Since 2011, the annual number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}. The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real estate property, and higher valuations from realtors, a closer analysis of active valuations adds a local view of which conditions contribute to the valuation of a real estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

@@

The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million. This research paper intends to analyse real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models. Our research question is as follows: 
\begin{center}
 \textit{Which features are most relevant for predicting valuations of real estate properties in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset. Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model. As a result, the best performing model is chosen with a discussion of its usability.

@@

Within social data science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.

@@

Historically, big data has been a term reserved for data that was unable to be processed by extant software. However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data}. Annual Review of Sociology}. Today, big data is no longer too cumbersome to analyse. Matthew Salganik\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data. Salganik's tentative definition suggests that big data is not a single entity, but includes many different types of systems. Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated. Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing. It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system. This algorithmic confounding force the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
In the analysis of big data it is often useful to employ machine learning as it can identify and predict various non-linear relationships in big data sets, that otherwise would remain hidden. Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian. Hal R. \textit{Big data: New tricks for econometrics}}.\newline

@@

The contribution from the social sciences to machine learning help create new methods that will be able to utilise the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda}}. These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions. Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.

\subsection{An Ethical Overview}
The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights. Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}}. These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}. This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections. 2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms. 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research. This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits. 4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability. It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018. Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}. Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik. 2018).\newline
From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies. To this end, the European Parliament introduced the General Data Protection Regulation (GDPR). With its seven overarching principles the GDPR seeks to formalise the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}). These principles include and expand upon the principles found in the Belmont and Menlo Report. The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research. There is considerable evidence that point to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity. A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).

\section{Data Description \& Ethics}

@@

In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data. Drawing upon the European Comissions\footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's website were carefully considered. As a step to prevent the mosaic effect and in an effort to anonymise the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}}. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function. This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see Jupyter XX)}. 

@@

In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks labelled \textcolor{red}{XX and XX.} 

@@

Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real estate sales in Denmark and has access to unique features such as days-for-sale, price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}. Giving us unique insights into the pricing of real estate in all 98 municipalities of Denmark. 65,950 properties were for sale at the time of scraping.\newline
The scraping process was conducted on Friday the $23^{rd}$ of August 2019. Global Investigative Journalism Network. In order to scrape the data of interest we familiarised ourselves with the HTML-structure of Boliga. On the basis of these insights we constructed a code, which was able to scrape every page, containing information pertaining the currently listed real estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline
For each listed property, 34 features and the target variable (price) was collected. Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

3. The feature is poorly formatted and cannot efficiently be recreated. 
11 features are considered to be of interest.

@@

Categorical: & ForClosure, Type, Municipality, lotSize	 \\	

@@

\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}

@@

As Jupyter performs poorly when running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.

@@

\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	

@@

\paragraph{DAWA\newline}

\paragraph{Socioeconomic Factors\newline}
Socioeconomic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. The factors include income, reported crime, level of highest completed education, etc. These were transformed into ratios, by taking the total population in a given municipality into account.   
 \vspace*{5px} \newline
\begin{tabular}{c c}
\textit{Features obtained:}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\small (relative to population) & vocational\_educ,	 SHE, 	MHE, bachelors\_degree  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & LHE, avg\_municipal\_income\_2017, Total\_reported\_crime\\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
\end{tabular}\newline 
\footnotesize{\textit{All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}}. 
\normalsize
\subsection{Analysis of Scraping Logs}
Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk. This section will analyse the logs created in the scraping process, with the intention of ensuring the data quality.
\paragraph{Response Code\newline}
When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request. Figure 2 displays response codes for the duration of the web scrapings. Every request received a response code 200, making further evaluation of the response codes redundant.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{1log.png} 
  \label{fig:}
\end{figure}

\paragraph{Error Codes\newline}
Figure plots error codes received throughout the duration of the scrapings. Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors. The error code returned the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
\normalsize
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{2log.png} 
  \label{fig:}
\end{figure}
To understand the errors, a closer manual analysis of the log was performed on requests receiving errors. The errors occurred in random intervals and were subsequently followed by another request to an identical URL. Therefore, we assessed that these errors were due to connection problems or server traffic. Since the errors were corrected by a following request, it should not affect the research.

\paragraph{Server Response Times\newline}
An indicator of poor data quality is varying response times from the server being scraped. \textcolor{red}{Figure XC} plots changes in response times for the duration of the web scrapings. The three data sources all resulted in few variations of response time. Unusual response times has been assessed within the logs, to be caused by either a slow server connection, or due to larger quantities of data being requested. To validate the quality of data, manual control of the returned results and the website results was performed, without notice of significant corruptions in the data utilised in the research.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{3log.png} 
  \label{fig:}
\end{figure}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs,siunitx}
\usepackage{float}
\usepackage{caption}
\usepackage{footnote}
\makesavenoteenv{tabular}
\usepackage{tablefootnote}
\lhead{}
\rhead{}
\chead{Social Data Science, Summer 2019}

@@

\tableofcontents
\newpage
\section{Introduction}
This research paper regards listed Danish real estate property valuations. Since 2011, the annual number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}. The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real estate property, and higher valuations from realtors, a closer analysis of active valuations adds a local view of which conditions contribute to the valuation of a real estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

@@

The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million. This research paper intends to use machine learning to analyse real estate price valuations and which geographical and sociodemographic criteria affect valuations. Our research question is as follows: 
\begin{center}
 \textit{How can geographic and sociodemographic features be utilised to predict real estate property valuations in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset. Also, a section regarding the choice and optimisation of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model. As a result, the best performing model is chosen with a discussion of its usability.

@@

Within social data science there exist different definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.

@@

Historically, big data has been a term reserved for data that was unable to be processed by extant software. However, recent increases in computational power has enabled data processing of hitherto unheard data quantities\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data}. Annual Review of Sociology}. Today, big data is no longer too cumbersome to analyse. Matthew Salganik\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data. Salganik's tentative definition suggests that big data is not a single entity, but includes many different types of systems. Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated. Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing. It is therefore important for scientist to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system. This algorithmic confounding force the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
In the analysis of big data it is often useful to employ machine learning as it can identify and predict non-linear relationships in big data sets, that otherwise would remain hidden. Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian. Hal R. \textit{Big data: New tricks for econometrics}}.\newline

@@

The contribution from the social sciences to machine learning help create new methods that will be able to utilise the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda}}. These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions. Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions and avenues of research\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.

\subsection{Ethical Concerns in a Petabyte Age}
The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights. Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}}. These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic Oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic Oath, says academic.}}. This discussion is nothing new however, as a tentative reformulation of the Hippocratic Oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
Matthew Salganik offers four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections. 2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms. 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research. This principle stresses that is should not be a single stratum of society that bears the costs of the research while another stratum benefits. 4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability. It is worth noting that Popper’s tentative Hippocratic Oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the $17^{th}$ of March 2018. Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API. This allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and used the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}. Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form. The gathered information was used to examine how these networks and their actors' behavior co-evolve. Another example of misuge of data is the emotional contagion experiment from 2012, where approximately 700,000 Facebook users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik. 2018).\newline
From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies. To this end, the European Parliament introduced the General Data Protection Regulation (GDPR). With its seven overarching principles the GDPR seeks to formalise the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}). These principles include and expand upon the principles found in the Belmont and Menlo Report. The most important consideration, however, must be that even a dataset comprising tens of thousands observations involve human beings who must be protected from adverse side-effects of the social research. There is considerable evidence that points to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity. A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).

\section{Data Description \& Ethics}
In the following sections we will consider the ethical ramifications of our inquiry. We will focus our efforts on the contractual obligations laid down by Boliga's Terms \& Conditions and the more general ethical considerations a social scientist should consider before conducting research. Following this, will be a brief description of our data, how it was collected, cleaned and examined.

@@

In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data. Drawing upon the European Comission's\footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's website were carefully considered. As a step to prevent the mosaic effect and in an effort to anonymise the scraped data, only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
Informed consent has not been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}}. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function. This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see Jupyter). 

@@

In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks. 

@@

Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real estate sales in Denmark and has access to unique features such as days-for-sale, price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}. This gives unique insight into the pricing of real estate in all 98 municipalities of Denmark. 65,950 properties were for sale at the time of scraping.\newline
The scraping process was conducted on Friday the $23^{rd}$ of August 2019. In order to scrape the data of interest we familiarised ourselves with the network-structure of Boliga. On the basis of these insights we constructed a code which was able to scrape every page, containing information on the currently listed real estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline
For each listed property, 34 features and the target variable (price) was collected. Appendix \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

3. The feature is poorly formatted and cannot efficiently be recreated. \newline
10 features are considered to be of interest.

@@

Categorical: & ForClosure, Type, Municipality	 \\	

@@

\paragraph{\href{https://www.hvorlangterder.dk}{hvorlangterder.dk}\newline}

@@

As Jupyter performs poorly when running long asynchronous tasks and the estimated running time was 18 hours, this procedure was run in Visual Studio Code.

@@

\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction \\	

@@

\paragraph{DAWA\newline}
\href{https://dawa.aws.dk/}{Denmark's Addresses Web API}\footnote{red. Danmarks Adressers Web API} (DAWA) is an API containing data regarding Danish addresses. DAWA will be used to collect information about the municipality that each address is located in. This data will be used to merge the socio-demographic data collected from various sources (see below) with the data scraped from Boliga.

\paragraph{Sociodemographic Factors\newline}
Sociodemographic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}. The factors include income, reported crime, level of highest completed education, etc. These were transformed into ratios, by taking the total population in a given municipality into account.   
 \vspace*{5px} \newline
\begin{tabular}{c c}
\textit{Features obtained}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\small (relative to population) & vocational\_educ,	 SHE, 	MHE, bachelors\_degree  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & LHE, avg\_municipal\_income\_2017, Total\_reported\_crime\\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
\end{tabular}\newline 
\footnotesize{\textit{All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}}. 
\normalsize
\subsection{Analysis of Scraping Logs}
Three datasets were obtained through web scraping from Boliga.dk, hvorlangterder.dk and DAWA.dk. This section will analyse the logs created in the scraping process, with the intention of ensuring the data quality.
\paragraph{Response Code\newline}
When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request. Figure 2 displays response codes for the duration of the web scrapings. Every request received a response code 200, making further evaluation of the response codes redundant.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{1log.png} 
  \label{fig:}
\end{figure}

\paragraph{Error Codes\newline}
Figure 3 plots error codes received throughout the duration of the scrapings. Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors. The error code returned the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
\normalsize
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{2log.png} 
  \label{fig:}
\end{figure}
To understand the errors, a closer manual analysis of the log was performed on requests receiving errors. The errors occurred in random intervals and were subsequently followed by another request to an identical URL. Therefore, we assessed that these errors were due to connection problems or server traffic. Since the errors were corrected by a following request, it should not affect the research.

\paragraph{Server Response Times\newline}
An indicator of poor data quality is varying response times from the server being scraped. Figure 4 plots changes in response times for the duration of the web scrapings. The three data sources all resulted in few variations of response time. Unusual response times have been assessed, to be caused by a slow server connection, or due to larger quantities of data being requested. To validate the quality of data, manual control of the returned results and the website results was performed, without notice of significant corruptions in the data.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{3log.png} 
  \label{fig:}
\end{figure}

\paragraph{Response Sizes\newline}
To validate the response quality, an assessment of the response size was performed. Figure 5 plots response sizes throughout the duration of the web scrapings. Boliga contains a single noticeably large response size within short time, while hvorlangterder response sizes vary throughout the scrape. The DAWA scrape resulted in consistent response sizes, and therefore needed no further investigation. 
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{4log.png} 
  \label{fig:}
\end{figure}
Examining the distribution of sample sizes in figure 6, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log. By manually assessing the returned output of the Boliga scrape, these two requests were found to return a larger amount of data than usual. The requests were made to two pages, where a few properties contained nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column. These dictionaries were image descriptions, and were not utilised within this research. These larger responses were deemed as not polluting the results of the research.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{5log.png} 
  \label{fig:}
\end{figure}
Figure 6 depicts that the hvorlangterder response sizes were a bit left skewed, while Figure 5 shows that the distribution of large sizes happens during the middle of the scrape. With a further glimpse into the log, we observed two things. Firstly, all response sizes of 0 are related to the errors, displayed in figure 2. The variance of responses could be explained by the type of data retrieved from the scrape. The request was set to return names, addresses, distances and other information, which sizes are varying in nature. When extracting the value from every single key of the dictionary output, no errors or missing values were found. Further control of samples of large and small sizes was performed without discovering flaws. The response sizes from hvorlangterder are found to vary in nature, which may explain the difference.
